Haploid Selection, Sex Ratio Bias, and Transitions Between Sex-Determination Systems

### 2017-09-28 LaTeX/Turnover.tex
ploidally antag region plots added

@@

\textcolor{red}{
Perhaps it would also be useful to add an 8 panel figure that features ploidally antagonistic selection. For each type of haploid selection (gametic competition/ meiotic drive in males/females), give a regionplot where $h^\male=h^\female$, e.g., $h^\male=h^\female=0.75$ (or perhaps the value of $h$ we use in the regionplots we have, in which $w_{aa}=0.85$, $w_{Aa}=1$, $w_{AA}=1.05$). 
Matt made a figure like this before but both Y$a$ and Y$A$ equilibria were plotted and there was no outline showing where the Y$a$ equilibrium is stable (as in Figure \ref{fig:regionplots}). In Matts plot the axes were $s^\Hermaphrodite$ and $\alpha_{\Delta}^\Hermaphrodite$. 
Add an asterisk to each region plot and show invasion in another panel, using those parameters and various $R$ (e.g., in the stye of \ref{fig:temporalOverdominance}). 
In an email, Sally has an example of ploidally-antagonistic selection where the neo-W fixes and $R=1/2$. This would cover that case and more. }

\textcolor{red}{
We could also give versions of Figure \ref{fig:regionplots} where there is also haploid selection of various types.
Haploid selection can favour $A$ or $a$, so this would involve 4x 6-panel figures. Started looking at this in Figure \ref{fig:regionMaleGS} and Figure \ref{fig:regionMaleDrive}, add female haploid selection. 
Try to integrate into the discussion of haploid selection? e.g., male haploid selection ones generally show effect of sex ratio, increasing both lambdas when female biased (top rows).}

>>>>

\begin{figure}[!h]
\centering
\centerline{\includegraphics[width=0.35\linewidth]{Region_plot_combined_PloidAntag_Matt}}
\caption{
$h=0.75$
}
\label{fig:regionPloidAntag}
\end{figure}

@@

\textcolor{red}{
Perhaps it would also be useful to add an 8 panel figure that features ploidally antagonistic selection. For each type of haploid selection (gametic competition/ meiotic drive in males/females), give a regionplot where $h^\male=h^\female$, e.g., $h^\male=h^\female=0.75$ (or perhaps the value of $h$ we use in the regionplots we have, in which $w_{aa}=0.85$, $w_{Aa}=1$, $w_{AA}=1.05$). 
Matt made a figure like this before but both Y$a$ and Y$A$ equilibria were plotted and there was no outline showing where the Y$a$ equilibrium is stable (as in Figure \ref{fig:regionplots}). In Matts plot the axes were $s^\Hermaphrodite$ and $\alpha_{\Delta}^\Hermaphrodite$. 
Add an asterisk to each region plot and show invasion in another panel, using those parameters and various $R$ (e.g., in the stye of \ref{fig:temporalOverdominance}). 
In an email, Sally has an example of ploidally-antagonistic selection where the neo-W fixes and $R=1/2$. This would cover that case and more. }
\textcolor{blue}{
did the region plots (Figure \ref{fig:regionPloidAntag}), yet to add the temporal dynamics
}

\textcolor{red}{
We could also give versions of Figure \ref{fig:regionplots} where there is also haploid selection of various types.
Haploid selection can favour $A$ or $a$, so this would involve 4x 6-panel figures. Started looking at this in Figure \ref{fig:regionMaleGS} and Figure \ref{fig:regionMaleDrive}, add female haploid selection. 
Try to integrate into the discussion of haploid selection? e.g., male haploid selection ones generally show effect of sex ratio, increasing both lambdas when female biased (top rows).}
\textcolor{blue}{
these figures are now done (ensuring frequencies between 0 and 1), but yet to discuss in text.}
